%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt, a4paper, twoside]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[francais]{babel}
\usepackage{lmodern}
\usepackage[margin=0.8in]{geometry}

\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{mathtools}
\usepackage{enumitem}
\usepackage{graphicx}
\usepackage[all]{xy}

\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\input{macrosMath}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
\title{Hand in 1}
\author{Christophe Marciot}
\maketitle

\section*{Exercise 6}
Suppose we have a natural transformation $\tau:F\rightarrow G$. We want to associate to $\tau$ a functor $H_\tau:\cC\times[1]\rightarrow\cD$ in a meaningful way. In fact we want that this association to remind us of the notion of homotopy in regular homotopy theory. \\
We propose the follwing definition. For an object $(c,x)\in \Ob\cC\times[1]$ and an arrow $(f,p)\in \Ob\cC\times[1]((c,x),(c',x'))$ we set their image by $H_\tau$:
	\begin{align*}
		H_\tau(c,x)=
			\begin{cases}
				F(c) &  \mathrm{if}\ x=0,\\
				G(c) & \mathrm{if}\ x=1
			\end{cases}
	\end{align*}
and 
	\begin{align*}
		H_\tau(f,p)=
			\begin{cases}
				F(f)  & \mathrm{if}\ p=0\leq0,\\
				\tau_{c'}F(f)=G(f)\tau_c & \mathrm{if}\ p=0\leq1,\\
				G(f) & \mathrm{if}\ p=1\leq1.
			\end{cases}
	\end{align*}
Note that the equalitiy in the second line is due to the fact that $\tau$ is a natural transformation.\\
 First, we need to prove that $H_\tau$ is a functor. Let us consider the identity $\Id_{(c,x)}=(\Id_c,x\leq x)$. We want to prove that $H_\tau(\Id_{(c,x)})=\Id_{H_\tau(c,x)}$. We distinguish two cases:
 	\begin{itemize}
		\item[$\bullet$] \underline{If $x=0$}: Then we get that $H_\tau(\Id_{(c,0)})=H_\tau(Id_c,0\leq0)=F(\Id_c)=\Id_{F(c)}=\Id_{H_\tau(c,0)}.$
		\item[$\bullet$] \underline{If $x=1$}: Then we get that $H_\tau(\Id_{(c,1)})=H_\tau(Id_c,1\leq1)=G(\Id_c)=\Id_{G(c)}=\Id_{H_\tau(c,1)}.$
	\end{itemize}
 Note that the third equalities are given by the fact that $F$ and $G$ are functors. Secondly, we need to prove that $H_\tau$ respects composition. Suppose we have $\xymatrix{(c,x)\ar[r]^{(f,p)}& (c',x')\ar[r]^{(f',p')}& (c'',x'')}$. We consider the following cases:
 	\begin{itemize}
		\item[$\bullet$] \underline{If $p=p'=0\leq0$}: We have $$H_\tau((f',0\leq0)(f,0\leq0))=H_\tau(f'f,0\leq0)=F(f'f)=F(f')F(f)=H_\tau(f',0\leq0)H_\tau(f,0\leq0).$$
		\item[$\bullet$] \underline{If $p=p'=1\leq0$}: We have $$H_\tau((f',1\leq1)(f,1\leq1))=H_\tau(f'f,1\leq1)=F(f'f)=F(f')F(f)=H_\tau(f',1\leq1)H_\tau(f,1\leq1).$$
		\item[$\bullet$] \underline{If $p=0\leq0$ and $p'=0\leq1$}: We have $$H_\tau((f',0\leq1)(f,0\leq0))=H_\tau(f'f,0\leq1)=\tau_{c''}F(f'f)=(\tau_{c''}F(f'))F(f)=H_\tau(f',0\leq1)H_\tau(f,0\leq0).$$
		\item[$\bullet$] \underline{If $p=0\leq1$ and $p'=1\leq1$}:  We have $$H_\tau((f',1\leq1)(f,0\leq1))=H_\tau(f'f,0\leq1)=G(f'f)\tau_{c}=G(f')(G(f)\tau_{c})=H_\tau(f',1\leq1)H_\tau(f,0\leq1).$$
	\end{itemize}
	(Note that the third and fourth cases are actually the same). This proves that $H_\tau$ is a functor. Now, thirdly, we need to prove that $H_\tau$ respects the wanted commutative property. We have that
	$$\begin{cases}
		 H_\tau\circ\Id_\cC\times{0}(c)=H_\tau(c,0)=F(c), \\
		 H_\tau\circ\Id_\cC\times{1}(c)=H_\tau(c,1)=G(c), \\
		 H_\tau\circ\Id_\cC\times{0}(f)=H_\tau(f,0\leq0)=F(f), \\
		 H_\tau\circ\Id_\cC\times{1}(f)=H_\tau(f,1\leq1)=G(f)
	\end{cases}$$
	for each $c\in\Ob\cC$ and $f\in\Mor\cC$. So the commutativity criterion is respected.\newpage
	
Now, let $H\in\Fun_{F,G}(\cC\times[1],\cD)$. We want to associate to $H$ a natural transformation $\tau_H$ from $F$ to $G$. The natural thing to do seems to set $(\tau_H)_c=H(\Id_c,0\leq1)$ for each $c\in\Ob\cC$.We then need to show that this defines a natural transformation. Let $c,d\in\Ob\cC$ and $f\in\cC(c,d)$. We need to show that 
	\begin{displaymath}
		\xymatrix{
			F(c) \ar[r]^{(\tau_H)_c} \ar[d]_{F(f)} & G(c) \ar[d]^{G(f)}\\
			F(d) \ar[r]_{(\tau_H)_d} & G(d)
		}
	\end{displaymath}
commutes. This said we have that 
	\begin{displaymath}
		G(f)(\tau_H)_c=H(f,1\leq1)H(\Id_c,0\leq1)=H(f,0\leq1)=H(\Id_d,0\leq1)H(f,0\leq0)=(\tau_H)_dF(f)
	\end{displaymath} 
and thus the diagram commutes and we have that $\tau_H$ is a natural transformation.\\\\
Lastly, we need to prove that these associations are inverses of each other, i.e. $H_{\tau_H}=H$ for each $H\in\Fun_{F,G}(\cC\times[1],\cD)$ and $\tau_{H_\tau}=\tau$ for each $\tau\in\Nat(F,G)$. For $H\in\Fun_{F,G}(\cC\times[1],\cD)$, $(c,x),(d,y)\in\Ob\cC\times[1]$ and $(f,p)\in\Ob\cC\times[1]((c,x),(d,y))$, we have that 
	\begin{align*}
		H_{\tau_H}(c,x) &=
			\begin{cases}
				F(c)=H(c,0) & \mathrm{if}\ x=0,\\
				G(c)=H(c,1) & \mathrm{if}\ x=1.
			\end{cases}\\
		H_{\tau_H}(f,p) &=
			\begin{cases}
				F(f) = H(f,0\leq0) & \mathrm{if}\ p=0\leq0,\\
				(\tau_H)_dF(f)=H(\Id_d,0\leq1)H(f,0\leq0)=H(f,0\leq1) & \mathrm{if}\ p=0\leq1,\\
				G(f)  = H(f,1\leq1) & \mathrm{if}\ p=1\leq1..
			\end{cases}
		\end{align*}
	We clearly see that $H_{\tau_H}$ is equal to $H$. Lastly, let $\tau\in\Nat(F,G)$. Then 
		\begin{displaymath}
			(\tau_{H_\tau})_c=H_\tau(\Id_c,0\leq1)=\tau_c
		\end{displaymath}
			for each $c\in\Ob\cC$ and thus we get that $\tau_{H_\tau}$ is equal to $\tau$. We can then conclude that those assignations are inverses to each other and define bijective maps between $\Nat(F,G)$ and $\Fun_{F,G}(\cC\times[1],\cD)$.
	
\end{document}
